### 2019-12-17 tex/ms.tex
fill in blank figure captions

\begin{center}
\Large
DESI GFA Throughput Validation
\end{center}

@@

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{zp_adu_gain_correlation-EF.png}
    \caption{test}
    \label{fig:ampsEF}
\end{figure*}

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{zp_adu_gain_correlation-GH.png}
    \caption{test}
    \label{fig:ampsEF}
\end{figure*}

@@

\section{Per-camera, per-amp scatter plots}

>>>>

\begin{center}
\Large
DESI GFA Zeropoints and Throughput Validation
\end{center}

@@

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{zp_adu_gain_correlation-EF.png}
    \caption{If we assume that the vignetting, QE, and filter transmission are the same for amps E and F within each guide camera, then the differences between the measured ADU zeropoints between these two amps within each guide camera should simply trace the differences in gain. Based on these assumptions and the the known ratio of gains in amps E and F, we can make a per-camera prediction of the difference in ADU zeropoints between amp E and amp F. This predicted ADU zeropoint difference is the horizontal axis in this plot. The measured difference in ADU zeropoints between amps E and F is then plotted on the vertical axis. Each white plus mark represents a single guide GFA camera. The red line is y = x, not a fit. For this exercise, we again use the lab-measured acceptance GFA gains. The measured zeropoint  differences between amps E and F do indeed trace the line y = x well --- the measured ADU zeropoints pass this sanity check.}
    \label{fig:ampsEF}
\end{figure*}

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{zp_adu_gain_correlation-GH.png}
    \caption{Same as Figure \ref{fig:ampsEF}, but for amps G and H.}
    \label{fig:ampsEF}
\end{figure*}

@@

\section{Per-camera, Per-amp Photometry Scatter Plots}
